[Re] Marriage and happiness: Providing evidence against a relationship between inequality and happiness in Oishi, Kesebir, and Diener (2011)

### 2020-03-15 analysis/paper.Rmd
Adding compendium

---
title: "[Re] Marriage and happiness: Providing evidence against a relationship between inequality and happiness in Oishi, Kesebir, and Diener (2011)"
author: "Lauren Heintz, Tara Wilson, Ben Mathieu, Will Wright"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
bibliography: bibliography.bibtex
link-citations: yes

@@

# The Gini indices come from the provided dataset
gini <-  read.csv("../data/Gini_families.csv") %>%
  select(year = Year, gini = Total)

@@

```{r, figure3, fig.cap="Figure 3 from the original paper", echo=FALSE}
knitr::include_graphics("original_paper_figure_3.png")
```

>>>>

---
title: "[Re] Marriage and happiness: Providing evidence against a relationship between inequality and happiness in Oishi, Kesebir, and Diener (2011)"
author: "Lauren Heintz, Tara Wilson, Ben Mathieu, Will Wright"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
bibliography: bibliography.bibtex
link-citations: yes
---

@@

# The Gini indices come from the provided dataset
gini <-  read.csv("data/Gini_families.csv") %>%
  select(year = Year, gini = Total)

@@

```{r, figure3, fig.cap="Figure 3 from the original paper", out.width="400px", echo=FALSE}
knitr::include_graphics("original_paper_figure_3.png")
```
